sfislands: An R Package for Accommodating Islands and Disjoint Zones in Areal Spatial Modelling

### 2024-03-03 article.Rmd
explain saved file use

@@

```{r}
# liverpool_hsamodel <- gam(unemployment ~ lt_illness +
#                          s(msoa_cd, bs="re") +
#                          s(msoa_cd, lt_illness, bs="re") +
#                          s(lsoa_cd, bs="re") +
#                          s(lsoa_cd, lt_illness, bs="re") +
#                          s(oa_cd, bs='mrf',
#                            xt=list(nb=prepliv$nb),k=20), # ICAR constituency ICAR varying coefficients
#                        data=prepliv, method="REML")

>>>>

# these models take a while to run
# so i am using a saved version of their output
# the files are large so are not on github
# uncomment the model and run it to reproduce

@@

# these models take a while to run
# so i am using a saved version of their output
# the files are large so are not on github
# uncomment the model and run it to reproduce

# liverpool_hsamodel <- gam(unemployment ~ lt_illness +
#                          s(msoa_cd, bs="re") +
#                          s(msoa_cd, lt_illness, bs="re") +
#                          s(lsoa_cd, bs="re") +
#                          s(lsoa_cd, lt_illness, bs="re") +
#                          s(oa_cd, bs='mrf',
#                            xt=list(nb=prepliv$nb),k=20), # ICAR constituency ICAR varying coefficients
#                        data=prepliv, method="REML")
